|

### 2023-01-29 paper_comparison/paper_comparison/paper_comparison.Rmd
replace CI band with lines

```{r}
# Get bootstrap CI
get_boot_conf <- function(dat, 
                          .x,
                          .y,
                          times = 100, 
                          upper_q = 0.975, 
                          lower_q = 0.025) {

@@

  # Draw bootstrap CI for visual test
  geom_ribbon(data = ~get_boot_conf(.x,
                                    log_effect_size,
                                    reject,
                                    times = 1000),
              aes(x = log_effect_size, 
                  ymin = lower, 
                  ymax = upper),
              fill = rev(rcartocolor::carto_pal(4, "Vivid"))[4],
              alpha = 0.2) +

@@

# Obtain data at different effect. Reuse x and recompute e.
for (i in target_sigma) {
  j <- j + 1
plist[[j]] <- poly_model(shape = 2, 
                         x = rand_uniform())$
                  gen(n = 100, 
                      computed =  ex_dat %>%
                        mutate(e = sqrt(i) * e) %>%
                        select(x, e)
                      ) %>%
  VI_MODEL$plot(theme = theme_light(base_size =  5), 
                remove_axis = TRUE, 
                remove_grid_line = TRUE, 
                size = 0.05) +
    ggtitle(round(es[j], 1)) +
    theme(aspect.ratio=0.8)
}

>>>>

```{r}
# Get bootstrap samples
get_boot_sample <- function(dat, times = 100) {
  map_df(1:times, 
         ~slice_sample(dat, n = nrow(dat), replace = TRUE) %>%
           mutate(boot_id = .x))
}

# Get bootstrap CI
get_boot_conf <- function(dat, 
                          .x,
                          .y,
                          times = 100, 
                          upper_q = 0.975, 
                          lower_q = 0.025) {

@@

  # Draw bootstrap CI for visual test
  # geom_ribbon(data = ~get_boot_conf(.x,
  #                                   log_effect_size,
  #                                   reject,
  #                                   times = 1000),
  #             aes(x = log_effect_size, 
  #                 ymin = lower, 
  #                 ymax = upper),
  #             fill = rev(rcartocolor::carto_pal(4, "Vivid"))[4],
  #             alpha = 0.2) +

  stat_smooth(data = ~get_boot_sample(.x, times = 1000),
              geom = "line",
              aes(log_effect_size, 
                  reject, 
                  col = "Visual test", 
                  group = boot_id),
              method = "glm",
              method.args = list(family = binomial),
              se = FALSE,
              alpha = 0.01) +

@@

# Obtain data at different effect. Reuse x and recompute e.
for (i in target_sigma) {
  j <- j + 1
plist[[j]] <- poly_model(shape = 2, 
                         x = rand_uniform())$
                  gen(n = 100, 
                      computed =  ex_dat %>%
                        mutate(e = sqrt(i) * e) %>%
                        select(x, e)
                      ) %>%
  VI_MODEL$plot(theme = theme_light(base_size =  5), 
                remove_axis = TRUE, 
                remove_grid_line = TRUE, 
                size = 0.05) +
    ggtitle(round(es[j], 1)) +
    theme(aspect.ratio = 0.8)
}
